Response to Reviewers and Associate Editor

### 2021-10-02 paper/changes.tex
Add files via upload
Added RMSE values in main paper, references in changes.pdf

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption, tabularx}
\usepackage{xcolor}
\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART) and Simultaneous
 Algebraic Reconstruction Technique (SART). We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART) since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT),
 Total Variation (TV) and Compressed Sensing (CS) with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{asfdaf}. The optimization routine we use
  transforms the reconstruction values to a different range of
  numerical values.  That is, in our experiments, we observed that for
  a given dataset and a set of projection measurements, the intensity
  span of histograms of reconstructed volumes differ considerably across various
  methods and solvers.  As a result, the RMSE values are not
  particularly useful, and may even be misleading.  We provide the RMSE numbers below to show the
  improvement trend but we believe it does not serve the interest of
  the community to report these in the main paper.

@@

  For the record, sample RMSE values are presented
  here in Tables~\ref{table:potato_rmse} and~\ref{table:sprouts_rmse} that shows
  the superiority of method at the risk of misleading absolute numbers.

@@

\begin{table}[!h]
  \centering
 \caption{RMSE within the RoI of 3D reconstructed Potato volume from various
    methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline 
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline  0.29 & 0.24 & \textcolor{red}{0.18}
\\ \hline
\end{tabular}
\label{table:potato_rmse}
\end{table}

\begin{table}[!h]
  \centering
 \caption{RMSE within the RoI of 3D reconstructed Sprouts volume from various
    methods.}
\begin{tabular}{|l|c|c|c|c|}
\hline 
\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline  0.53 & 0.48 & \textcolor{red}{0.30}
\\ \hline
\end{tabular}
\label{table:sprouts_rmse}
\end{table}

@@

\end{document}

>>>>

\documentclass{article}
\bibliographystyle{IEEEtran}

\usepackage{amsmath}
\usepackage{graphicx}
\bibliographystyle{IEEEtran}
\usepackage{caption}
\usepackage{subcaption, tabularx}
\usepackage{xcolor}
\usepackage{boxedminipage}
\usepackage{a4wide}
\usepackage{subcaption}
\usepackage[colorlinks=true]{hyperref}
\title{Response to Reviewers and Associate Editor}
\begin{document}
\date{}
\maketitle

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. We do not reconstruct
 using Discrete Algebraic Reconstruction Technique (DART)~\cite{dart} since there
 is no prior information about the number of possible attentuation
 coefficients in the test object.
%% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

  The reason for not reporting RMSE stems from the optimization
  process in Equation~\ref{Eq:simple_TV}.

 \begin{equation}
   J_{TV}(\boldsymbol{x}) = \lVert\boldsymbol{\mathcal{R}x}- \boldsymbol{y}\rVert_2^2 + \lambda_{TV}TV(\boldsymbol{x})
   \label{Eq:simple_TV}
 \end{equation}

  This optimization routine 
  transforms the reconstruction values to a different range of
  numerical values.  That is, in our experiments, we observed that for
  a given dataset and a set of projection measurements, the intensity
  span of histograms of reconstructed volumes differ considerably across various
  methods and solvers.  As a result, the RMSE values are not
  particularly useful, and may even be misleading.  We provide the RMSE numbers below to show the
  improvement trend but we believe it does not serve the interest of
  the community to report these in the main paper.

@@

  For the record, sample RMSE values are presented
  here in Table~\ref{table:rmse} that shows
  the superiority of our method at the risk of misleading absolute numbers.

@@

\begin{table}[!h]
  \centering
 \caption{RMSE of reconstructions from various
    methods within the RoI.}
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
&\textbf{Backprojection} & \textbf{TV} & \textbf{This paper}
\\ \hline \textbf{Potato}& 0.29 & 0.24 & \textcolor{red}{0.18}
\\ \hline \textbf{Sprouts}& 0.53 & 0.48 & \textcolor{red}{0.30}
\\ \hline \textbf{Liver}& 0.05 & 0.17 & \textcolor{red}{0.03}
\\ \hline
\end{tabular}
\label{table:rmse}
\end{table}

@@

\bibliography{tci_ref}  
\end{document}
